\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/conclude.tex
backend to implementation
nit
final edits

\section{Conclusion}
\label{sec:conclude}
We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works.
The \mpc backed we use provides security against semi-honest or passive adversaries.
%our compiler is oblivious to the ``type of adversary'' for the underlying \mpc backend.
Given a \mpc backend secure against malicious or active adversaries, Theorem \ref{theorem:security} 
can be extended to obtain a framework with malicious security. Furthermore,  
partitioning can be modified to provide malicious security by {\it signing} the shares of the intermediate states. However, we are not aware of a maliciously secure \mpc backend that works with combinations of
arithmetic and boolean circuits.

>>>>

\section{Conclusion}
\label{sec:conclude}
We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the custom, specialized
protocols from previous works.
The \mpc backed we use provides security against semi-honest or passive adversaries.
%our compiler is oblivious to the ``type of adversary'' for the underlying \mpc backend.
Given a \mpc backend secure against malicious or active adversaries, Theorem \ref{theorem:security} 
can be extended to obtain a framework with malicious security. Furthermore,  
partitioning can be modified to provide malicious security by {\it signing} the shares of the intermediate states. However, we are not aware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.

### 2017-10-31 OaklandSubmission/ex.tex
final edits

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). E.g., in Figure~\ref{fig:ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

>>>>

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). For example, in Figure~\ref{fig:ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

### 2017-10-31 OaklandSubmission/intro.tex
final edits

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a, general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

Alternatively, Alice can use a tool such as ABY (Demmler et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

>>>>

 Today it is hard for developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a, general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

Alternatively, Alice can use a tool such as ABY (Demmler et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
subject to errors (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

### 2017-10-31 OaklandSubmission/main.tex
minor
smcl
appendix commented
authors
final edits

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Michael Shell}
% \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
% Georgia Institute of Technology\\
% Atlanta, Georgia 30332--0250\\
% Email: http://www.michaelshell.org/contact.html}
% \and
% \IEEEauthorblockN{Homer Simpson}
% \IEEEauthorblockA{Twentieth Century Fox\\
% Springfield, USA\\
% Email: homer@thesimpsons.com}
% \and
% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
% \IEEEauthorblockA{Starfleet Academy\\
% San Francisco, California 96678-2391\\
% Telephone: (800) 555--1212\\
% Fax: (888) 555--1212}}

@@

  %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
\mpc protocols from high-level, easy-to-write programs.
\tool provides formal correctness and security guarantees while maintaining performance and scalability.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
Previous language frameworks such as Wysteria, ObliVM, CBMC-GC, etc. generate protocols that use either arithmetic or boolean circuits exclusively. Our compiler is the first to generate protocols that combine both arithmetic sharing and garbled circuits  for better performance.
%We give the first compiler that generates protocols which combine both arithmetic and boolean circuits
%for better performance compared to protocols that use either arithmetic or boolean circuits exclusively.
We
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x)
recent works that provide hand-crafted protocols for various
functionalities such as secure  prediction  and matrix factorization.
%\tool provides formal correctness and security guarantees.
%% (up to
%% a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

@@

\appendix
\input{app-stash}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Nishanth Chandran \hspace{10pt} Divya Gupta  \hspace{10pt} Aseem Rastogi \hspace{10pt}  Rahul Sharma \hspace{10pt} Shardul Tripathi }
% \IEEEauthorblockA{Microsoft Research India}
%}

@@

  %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
\mpc protocols from high-level, easy-to-write, programs.
\tool provides formal correctness and security guarantees while maintaining performance and scalability.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
Previous language frameworks such as CBMC-GC, ObliVM, SMCL, and Wysteria, generate protocols that use either arithmetic or boolean circuits exclusively. Our compiler is the first to generate protocols that combine both arithmetic sharing and garbled circuits  for better performance.
%We give the first compiler that generates protocols which combine both arithmetic and boolean circuits
%for better performance compared to protocols that use either arithmetic or boolean circuits exclusively.
We
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x)
recent works that provide hand-crafted protocols for various
functionalities such as secure  prediction  and matrix factorization.
%\tool provides formal correctness and security guarantees.
%% (up to
%% a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

@@

%\appendix
%\input{app-stash}

### 2017-10-31 OaklandSubmission/related.tex
color
final edits

Next, we discuss tools that expose libraries which  developers can use to describe \mpc protocols. 
% The exact cryptographic protocols that are used by the library  need not be known to the programmer. However, in order 
To generate efficient protocols for a functionality, the programmer must break the functionality into components and call the appropriate library functions. For example,  ABY \cite{aby} falls in this category. The TASTY tool~\cite{tasty} allows mixing homomorphic encryption based arithmetic computations 
and garbled circuits based boolean computations and the interconversions between the two are inserted by the programmer explicitly.
% While, the programmer need not know how ABY implements boolean or arithmetic computation, he or she must know the type of compute (boolean or arithmetic) that is more efficient for specific sub-computations and also explicitly write calls to convert shares from one scheme to another (boolean secret sharing to arithmetic secret sharing and vice-versa). 
The work of Kerschbaum et al.~\cite{autoS} provides a scheme to automatically assign homomorphic encryption or garbled circuits to each operator in a computation that is expressed as a sequence of dyadic operations. They conjecture that the problem is NP hard and gave a linear programming based solution as well as a quadratic time greedy heuristic. 
These techniques are not directly applicable to \tool programs because of for-loops and if-conditions.
However, we are exploring whether these ideas can be extended to yield a better type inference.
%Their performance is much poorer than ABY due to the high 
%costs associated with homomorphic encryption~\cite{aby}.
%conversion costs between homomorphic encryption and boolean shares~\cite{aby}.  %On the other hand \tool uses a simpler constant time heuristic to assign arithmetic secret sharing or garbled circuits to sub-computations in a richer language with control flow statements such as loops and branches.
%While the work of Kerschbaum {\em et al.}~\cite{kos14} provides a heuristic to automatically select the protocol for various types of sub-computations, one would still need to manually write the program using the share conversion tools of ABY. Similarly, the TASTY tool~\cite{tasty} provides a way to mix both boolean and arithmetic circuits (using homomorphic encryption for the arithmetic compute). 
Other examples include the VIFF framework~\cite{viff} for arithmetic computations and Sharemind~\cite{sharemind} (that provides secure 3-party boolean computation). 
%\\\\
%\noindent{\bf Protocol Implementation:} Tools at this level of abstraction require the programmer to have a deep understanding of how cryptographic secure computation protocols work and the programmer must provide calls to low-level cryptographic building blocks such as oblivious transfer. For example while the programmer need not know the specific oblivious transfer protocol implemented in the backend, he or she still needs to know how to build a secure computation protocol from such building blocks. This abstraction requires the highest knowledge of cryptography from the programmer. Examples of such tools include L1~\cite{lone} and Qilin~\cite{qilin}.

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized, hand-crafted protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This process requires deep knowledge of cryptography
to ensure that the protocols are secure.
Examples include privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, private sequence analysis~\cite{franz}, private biometric identification~\cite{huang}, privacy-preserving matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

>>>>

Next, we discuss tools that expose libraries which  developers can use to describe \mpc protocols. 
% The exact cryptographic protocols that are used by the library  need not be known to the programmer. However, in order 
To generate efficient protocols for a functionality, the programmer must break the functionality into components and call the appropriate library functions. For example,  ABY \cite{aby} falls in this category. The TASTY tool~\cite{tasty} allows mixing homomorphic encryption based arithmetic computations 
and garbled circuits based boolean computations and the interconversions between the two are inserted by the programmer explicitly.
% While, the programmer need not know how ABY implements boolean or arithmetic computation, he or she must know the type of compute (boolean or arithmetic) that is more efficient for specific sub-computations and also explicitly write calls to convert shares from one scheme to another (boolean secret sharing to arithmetic secret sharing and vice-versa). 
The work of Kerschbaum et al.~\cite{autoS} provides a scheme to automatically assign homomorphic encryption or garbled circuits to each operator in a computation that is expressed as a sequence of dyadic operations. They conjecture that the problem is NP hard and gave a linear programming based solution as well as a quadratic time greedy heuristic. 
These techniques are not directly applicable to \tool programs because of $\mathtt{for}$-loops and $\mathtt{if}$-conditions.
However, we are exploring whether these ideas can be extended to yield a better type inference.
%Their performance is much poorer than ABY due to the high 
%costs associated with homomorphic encryption~\cite{aby}.
%conversion costs between homomorphic encryption and boolean shares~\cite{aby}.  %On the other hand \tool uses a simpler constant time heuristic to assign arithmetic secret sharing or garbled circuits to sub-computations in a richer language with control flow statements such as loops and branches.
%While the work of Kerschbaum {\em et al.}~\cite{kos14} provides a heuristic to automatically select the protocol for various types of sub-computations, one would still need to manually write the program using the share conversion tools of ABY. Similarly, the TASTY tool~\cite{tasty} provides a way to mix both boolean and arithmetic circuits (using homomorphic encryption for the arithmetic compute). 
Other examples include the VIFF framework~\cite{viff} for arithmetic computations and Sharemind~\cite{sharemind} (that provides secure 3-party boolean computation). 
%\\\\
%\noindent{\bf Protocol Implementation:} Tools at this level of abstraction require the programmer to have a deep understanding of how cryptographic secure computation protocols work and the programmer must provide calls to low-level cryptographic building blocks such as oblivious transfer. For example while the programmer need not know the specific oblivious transfer protocol implemented in the backend, he or she still needs to know how to build a secure computation protocol from such building blocks. This abstraction requires the highest knowledge of cryptography from the programmer. Examples of such tools include L1~\cite{lone} and Qilin~\cite{qilin}.

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized, hand-crafted protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure the security of the protocols.
Examples include privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, private sequence analysis~\cite{franz}, private biometric identification~\cite{huang}, privacy-preserving matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

### 2017-10-31 OaklandSubmission/security.tex
final edits

\noindent {\em Proof.} 
Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\crct$. It is crucial that this compilation to circuits does not require the secret inputs of the parties. Next, $\simu$ sends the input of the corrupt party to the trusted functionality of $s$ to obtain outputs $O_1$. Note that $O_1$ is same as the observations in the source semantics. 
By \theoremref{correctness}, these outputs $O_1$ are identical to outputs (or observations) $O_2$ of $\crct$ under circuit semantics. 
Next, $\simu$ runs $\simu_{\tiny{2pc}}$ on $\crct$, input of the corrupt party and $O_2$. 
From the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ is indistinguishable from the real view of the $\prot$ for $\crct$ between the two parties. Hence, the security follows.

>>>>

\noindent {\em Proof.} 
Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\crct$. It is crucial that this compilation to circuits does not require the secret inputs of the parties. Next, $\simu$ sends the input of the corrupt party to the trusted functionality of $s$ to obtain outputs $O_1$. Note that $O_1$ is same as the observations in the source semantics. 
By \theoremref{correctness}, these outputs $O_1$ are identical to outputs (or observations) $O_2$ of $\crct$ under circuit semantics. 
Next, $\simu$ runs $\simu_{\tiny{2pc}}$ on $\crct$, input of the corrupt party and $O_2$ (note, while $\simu_{\tiny{2pc}}$ expects output $O_1$ as its input, it is ok for $\simu$ to run $\simu_{\tiny{2pc}}$ on $O_2$ instead as $O_2=O_1$). 
From the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ is indistinguishable from the real view of the $\prot$ for $\crct$ between the two parties. Hence, the security follows.
